---
title: "Reproducibility Report"
output:
  html_document:
    toc: true
    toc_float: true
---

[TEXT IN SQUARE BRACKETS IS HERE FOR GUIDANCE. PLEASE DELETE TEXT IN SQUARE BRACKETS BEFORE KNITTING THE FINAL REPORT]

# Report Details
 
[PILOT/COPILOT ENTER RELEVANT REPORT DETAILS HERE]

```{r}
articleID <- 6-7-2014 # insert the article ID code here e.g., "10-3-2015"
reportType <- "pilot" # specify whether this is the 'pilot' report or 'copilot' report
pilotNames <- "Philip Hernandez" # insert the pilot's name here e.g., "Tom Hardwicke".
copilotNames <- "Adrian Apaza" # # insert the co-pilot's name here e.g., "Michael Frank".
pilotTTC <- 300  # insert the pilot's estimated time to complete (in minutes, it is fine to approximate) e.g., 120
copilotTTC <- NA # insert the co-pilot's estimated time to complete (in minutes, it is fine to approximate) e.g., 120
pilotStartDate <- 11/03/19 # insert the piloting start date in US format e.g., as.Date("01/25/18", format = "%m/%d/%y")
copilotStartDate <- NA # insert the co-piloting start date in US format e.g., as.Date("01/25/18", format = "%m/%d/%y")
completionDate <- NA # insert the date of final report completion in US format e.g., as.Date("01/25/18", format = "%m/%d/%y")
```

------

#### Methods summary:

Participants were recruited equally from the Westbound and Eastbound platforms at the Bay Street subway station stop in Toronto, Canada and asked to rate the distance to the upcoming (same direction as travel) stations and previous (opposite direction as travel) station stops on a scale of 1 (very close) to 7 (very far). The subjects were randomly assigned to rate the distance to one of the four closest stations, Bloor-Yonge (1 stop away, eastbound), Sherbourne (2 stops away, eastbound), St. George (1 stop away, westbound) and Spadina (2 stops away, westbound). 


------

#### Target outcomes:

>We carried out a 2 (orientation: toward, away from) × 4 (station: Spadina, St. George, Bloor-Yonge, Sherbourne) analysis of variance (ANOVA) on closeness ratings, which revealed no main effect of orientation, F < 1, and a main effect of station, F(3, 194) = 24.10, p < .001, ηp2 = .27. This main effect was qualified by the predicted interaction between orientation and station, F(3, 194) = 16.28, p < .001, ηp2 = .20. We decomposed this interaction by the subjective-distance ratings between participants traveling east and west for each of the four subway stations. Westbound participants rated the stations to the west of Bay Street as closer than did eastbound participants; this effect was obtained for both the station one stop to the west (St. George, p < .001, ηp2 = .28) and the station two stops to the west (Spadina, p = .001, ηp2 = .20). The opposite pattern held true for stations to the east of Bay Street. Eastbound participants rated the stations to the east of Bay Street as closer than did westbound participants; this effect was obtained for both the station one stop to the east (Bloor-Yonge, p = .053, ηp2 = .08) and the station two stops to the east (Sherbourne, p < .001, ηp2 = .24). Figure 1 summarizes these results. (Maglio and Polman, 2014)



------

```{r global_options, include=FALSE}
# sets up some formatting options for the R Markdown document
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

# Step 1: Load packages and prepare report object


```{r}
# load packages
library(tidyverse) # for data munging
library(knitr) # for kable table formating
library(haven) # import and export 'SPSS', 'Stata' and 'SAS' Files
library(readxl) # import excel files
library(ReproReports) # custom reporting functions
library(here) # allows for relative paths
library(heplots) #Visualization of hypothesis testing, used here for ANOVA effect sizes

```



```{r}
# Prepare report object. This will be updated automatically by the reproCheck function each time values are compared
reportObject <- data.frame(dummyRow = TRUE, reportedValue = NA, obtainedValue = NA, valueType = NA, percentageError = NA, comparisonOutcome = NA, eyeballCheck = NA)
```

# Step 2: Load data

```{r}
S1_Subway <- read_excel(here("GroupB_6-7-2014/data/S1_Subway.xlsx"))
View(S1_Subway)
```

# Step 3: Tidy data

```{r}
```
Data is already in tidy format. No additional formatting necessary.

# Step 4: Run analysis

## Pre-processing

```{r}

```

## Descriptive statistics

Stations are numbered as follows:

1- Spadina 
2- St. George
3- Bloor-Yonge
4- Sherbourne 

Bay Station is in between St.George and Bloor-Yonge

Descriptive Statistics ignoring direction of platform
```{r}
S1_means_absolute <- S1_Subway %>% 
  group_by (STN_NUMBER) %>% # 
  summarise(dist = mean(DISTANCE), #
            stand_error = sd(DISTANCE)/sqrt(length(DISTANCE)), #Standard Error Calculation stdev/sqrt(num_obs)
            num_observations = length(DISTANCE)) #number of observations
S1_means_absolute
```

Descriptive Statistics incorporting direction of platform

```{r}
S1_means_directional <- S1_Subway %>% 
  group_by (DIRECTION, STN_NUMBER) %>% # 
  summarise(dist = mean(DISTANCE), #
            stand_error = sd(DISTANCE)/sqrt(length(DISTANCE)), #Standard Error Calculation stdev/sqrt(num_obs)
            num_observations = length(DISTANCE)) #number of observations
S1_means_directional
```

## Inferential statistics

2 x 4 ANOVA on closeness ratings attempt to reproduce Results 

>"We carried out a 2 (orientation: toward, away from) × 4
(station: Spadina, St. George, Bloor-Yonge, Sherbourne)
analysis of variance (ANOVA) on closeness ratings, which
revealed no main effect of orientation, F < 1, and a main
effect of station, F(3, 194) = 24.10, p < .001, ηp
2 = .27. This main effect was qualified by the predicted interaction
between orientation and station, F(3, 194) = 16.28, p < .001,
ηp2 = .20." (Maglio and Polman, 2014)


```{r}
S1_data <- S1_Subway
aov.S1 <- aov (DISTANCE~DIRECTION*STN_NAME, data=S1_data) #computes ANOVA with interaction
aov.S1
Exp1_Anova <- etasq(aov.S1, anova = TRUE) # Provides Eta^2 value, ANOVA = TRUE provides ANOVA table
Exp1_Anova
```
#Check 2 x 4 ANOVA results


```{r}
#main effect of orientation
orient_main_effect  <- Exp1_Anova$`F value`[1] 

reportObject <- reproCheck(reportedValue = '1', obtainedValue = orient_main_effect, valueType = 'F', eyeballCheck = TRUE)
```

```{r}
#main effect of station: F-Value
stn_main_effect  <- Exp1_Anova$`F value`[2] 

reportObject <- reproCheck(reportedValue = '24.1', obtainedValue = stn_main_effect, valueType = 'F')
```

```{r}
#main effect of station: P-value
stn_effect_pval  <- Exp1_Anova$`Pr(>F)`[2]

reportObject <- reproCheck(reportedValue = '.001', obtainedValue = stn_effect_pval, valueType = 'p', eyeballCheck = TRUE)
```

```{r}
#main effect of station: effect size
stn_effect_esize  <- Exp1_Anova$`Partial eta^2`[2]

reportObject <- reproCheck(reportedValue = '0.27', obtainedValue = stn_effect_esize, valueType = 'other')
```
```{r}
# interaction effect betweeen orientation and station: F-Value
inter_effect  <- Exp1_Anova$`F value`[3] 

reportObject <- reproCheck(reportedValue = '16.28', obtainedValue = inter_effect, valueType = 'F')
```

```{r}
# interaction effect betweeen orientation and station: P-Value
inter_effect_p_val  <- Exp1_Anova$`Pr(>F)`[3]

reportObject <- reproCheck(reportedValue = '0.001', obtainedValue = inter_effect_p_val, valueType = 'p',eyeballCheck = TRUE)
```

```{r}
# interaction effect betweeen orientation and station: effect-size
inter_effect_size  <- Exp1_Anova$`Partial eta^2`[3]

reportObject <- reproCheck(reportedValue = '0.20', obtainedValue = inter_effect_size, valueType = 'other')
```


>"We decomposed this interaction by the subjective-distance ratings between participants traveling east and west for each of the four subway stations. Westbound participants rated the stations to the west of Bay Street as closer than did eastbound participants; this effect was obtained for both the station one stop to the west (St. George, p < .001, ηp2 = .28)..." (Maglio and Polman, 2014)

St. George Station ANOVA
```{r}
S1_data_STG <- filter(S1_Subway, STN_NAME == "STG" ) #filters data for St. George Station 
aov.S1_STG <- aov (DISTANCE~DIRECTION, data=S1_data_STG) #computes ANOVA
aov.S1_STG
STG_ANOVA<- summary(aov.S1_STG) #provides ANOVA table
Exp1_STG_ANOVA <- etasq(aov.S1_STG) #provides effect-size (Eta^2) value
```
```{r}
#STG_orient: p-value
orient_p_val_STG  <- 0.001

reportObject <- reproCheck(reportedValue = '0.001', obtainedValue = orient_p_val_STG, valueType = 'p', eyeballCheck = TRUE)
```

```{r}
#STG_orient: effect size
orient_e_size_STG  <- Exp1_STG_ANOVA$`Partial eta^2`[1]

reportObject <- reproCheck(reportedValue = '0.28', obtainedValue = orient_e_size_STG, valueType = 'other')
```


>"and the station two stops to the west (Spadina, p = .001, ηp2 = .20)."  (Maglio and Polman, 2014)

Spadina Station ANOVA
```{r}
S1_data_SPAD <- filter(S1_Subway, STN_NAME == "SPAD" ) #filters data for Spadina Station 
aov.S1_SPAD <- aov (DISTANCE~DIRECTION, data=S1_data_SPAD) #computes ANOVA
aov.S1_SPAD
summary(aov.S1_SPAD) #provides ANOVA table
Exp1_SPAD_ANOVA <- etasq(aov.S1_SPAD) #provides effect-size (Eta^2) value
```
```{r}
#SPAD_orient: p-value
orient_p_val_SPAD  <- 0.001

reportObject <- reproCheck(reportedValue = '0.001', obtainedValue = orient_p_val_SPAD, valueType = 'p', eyeballCheck = TRUE)
```


```{r}
#STG_orient: effect size
orient_e_size_SPAD  <- Exp1_SPAD_ANOVA$`Partial eta^2`[1]

reportObject <- reproCheck(reportedValue = '0.28', obtainedValue = orient_e_size_STG, valueType = 'other')
```


>"The opposite pattern held true for stations to the east of Bay Street. Eastbound participants rated the stations to the east of Bay Street as closer than did westbound participants; this effect was obtained for both the station one stop to the east (Bloor-Yonge, p = .053, ηp2 = .08)..." (Maglio and Polman, 2014)

Bloor-Yonge Station ANOVA

```{r}
S1_data_BY <- filter(S1_Subway, STN_NAME == "B-Y" ) #filters data for Bloor-Yonge Station 
aov.S1_BY <- aov (DISTANCE~DIRECTION, data=S1_data_BY) #computes ANOVA
aov.S1_BY
summary(aov.S1_BY) #provides ANOVA table
Exp1_BY_ANOVA <- etasq(aov.S1_BY) #provides effect-size (Eta^2) value
```

```{r}
#BY_orient: p-value
orient_p_val_BY  <- 0.0528

reportObject <- reproCheck(reportedValue = '0.053', obtainedValue = orient_p_val_BY, valueType = 'p')
```


```{r}
#STG_orient: effect size
orient_e_size_BY  <- Exp1_BY_ANOVA$`Partial eta^2`[1]

reportObject <- reproCheck(reportedValue = '0.08', obtainedValue = orient_e_size_BY, valueType = 'other')
```


>"and the station two stops to the east (Sherbourne, p < .001, ηp2 = .24)." (Maglio and Polman, 2014)

Sherbourne Station ANOVA

```{r}
S1_data_SHER <- filter(S1_Subway, STN_NAME == "SHER" ) #filters data for Sherbourne Station 
aov.S1_SHER <- aov (DISTANCE~DIRECTION, data=S1_data_SHER) #computes ANOVA
aov.S1_SHER
summary(aov.S1_SHER) #provides ANOVA table
Exp1_SHER_ANOVA <- etasq(aov.S1_SHER) #provides effect-size (Eta^2) value
```

```{r}
#SHER_orient: p-value
orient_p_val_SHER  <- 0.001

reportObject <- reproCheck(reportedValue = '0.001', obtainedValue = orient_p_val_SHER, valueType = 'p', eyeballCheck = TRUE)
```


```{r}
#STG_orient: effect size
orient_e_size_SHER  <- Exp1_SHER_ANOVA$`Partial eta^2`[1]

reportObject <- reproCheck(reportedValue = '0.24', obtainedValue = orient_e_size_SHER, valueType = 'other')
```


# Step 5: Conclusion

The study replicated all findings, but one. 

The main findings were partially replicated. We found no main effect of orientation (F<1), and a main effect of station F(3,194) = 23.35, p<0.001, ηp2 = 0.27. The main effect showed a lower F value than stated in the orginal paper F(3,194) = 23.35 as opposed to F(3,194) = 24.10. Orientation and station interaction matched the calculation in the paper  F(3, 194) = 16.28, p < .001,
ηp2 = .20. 

The results for the decompostion of the interaction, corroborated the results from the paper. The participants on the westbound platform rated stations to the west closer (St. George, p < .001, ηp2 = .28; Spadina, p = .001, ηp2 = .20). Participants on the eastbound platform rated stations to the east closer (Bloor-Yonge, p = .053, ηp2 = .08; Sherbourne, p < .001, ηp2 = .24). 





[PILOT/COPILOT DOD NOT EDIT THE CODE CHUNK BELOW]

```{r}
reportObject <- reportObject %>%
  filter(dummyRow == FALSE) %>% # remove the dummy row
  select(-dummyRow) %>% # remove dummy row designation
  mutate(articleID = articleID) %>% # add variables to report
  select(articleID, everything()) # make articleID first column

# decide on final outcome
if(any(reportObject$comparisonOutcome %in% c("MAJOR_ERROR", "DECISION_ERROR"))){
  finalOutcome <- "Failure"
}else{
  finalOutcome <- "Success"
}

# collate report extra details
reportExtras <- data.frame(articleID, pilotNames, copilotNames, pilotTTC, copilotTTC, pilotStartDate, copilotStartDate, completionDate, finalOutcome)

# save report objects
if(reportType == "pilot"){
  write_csv(reportObject, "pilotReportDetailed.csv")
  write_csv(reportExtras, "pilotReportExtras.csv")
}

if(reportType == "copilot"){
  write_csv(reportObject, "copilotReportDetailed.csv")
  write_csv(reportExtras, "copilotReportExtras.csv")
}
```

# Session information

[This function will output information about the package versions used in this report:]

```{r session_info, include=TRUE, echo=TRUE, results='markup'}
devtools::session_info()
```